### 2011-05-06 paper/paper.tex
more minor edits, also defined the word mixing

Thus, by \ref{symmetric}, both ball-walking and Gaussian-walking have a stationary uniform distribution.
\end{proof}

It is also shown in \cite{Smith} that the distributions from a Markov chain with a symmetric transition function eventually \emph{converge} to this stationary uniform distribution, which shows that these algorithms for sampling uniformly will work, given enough time. However, in the next section, we will see that this can take a very long time to converge, and we modify the algorithm in an attempt to fix this problem.

@@

\begin{theorem}[{\bf Hit-and-run bound}] \label{hitandrunbound} Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $P$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - P(r)| \le \epsilon$.\end{center}
\end{theorem}

>>>>

Thus, the transition functions are symmetric, so by \ref{symmetric}, both ball-walking and Gaussian-walking have a stationary uniform distribution.
\end{proof}

It is also shown in \cite{Smith} that the distributions from a Markov chain with a symmetric transition function eventually \emph{converge} to this stationary uniform distribution, which shows that these algorithms for sampling uniformly will work, given enough time. The \emph{mixing time} of an algorithm is the number of iterations required for the distribution to converge to the uniform distribution within some desired precision. Ideally, we want the mixing time to be small. However, in the next section, we will see that this can take a very long time to mix, and we modify the algorithm in an attempt to fix this problem.

@@

\begin{theorem}[{\bf Hit-and-run mixing bound}] \label{hitandrunbound} Suppose we are considering the hit-and-run Markov chain on an $n$-dimensional convex region $\mathcal{R}$, starting from a point of distance $d$ from the boundary of $\mathcal{R}$. Suppose $\mathcal{R}$ contains a ball of radius $r$ and is contained in a ball of radius $R$. Then after
\begin{center}$m = \displaystyle 10^{11}\frac{n^3 R^2}{r^2}\ln\frac{R}{d\epsilon}$\end{center}
steps, the total variation distance of the chain is within $\epsilon$ of the uniform distribution. That is, if $\mu$ is the uniform distribution and $P$ is the the distribution of the chain after $m$ steps, then
\begin{center}$\displaystyle \sup_{r \in \mathcal{R}} |\mu(r) - P(r)| \le \epsilon$.\end{center}
\end{theorem}
